%!TEX program = xelatex
\documentclass[UTF8]{ctexart}

\usepackage{color}
\usepackage[linkcolor=red,citecolor=red,backref=page]{hyperref}
\pagestyle{plain}
\begin{document}
\section{原文与翻译}
\subsection{Red-hot tips for black-tie beauty 出席场合，到底该怎么美妆？}

The number one tip for getting ready on the red carpet?” asks Cassandra Huysentruyt Grey, founder of LA beauty boutique Violet Grey: “Give yourself extra time to get comfortable in your look. You’re \colorbox{yellow}{thrown into}$^{\ref{voc:1}}$ this high-pressure environment and if you don’t feel comfortable it will show in your body language and all over your face.”

“走红毯的首要美妆诀窍是什么？”洛杉矶Violet Grey美容院创始人卡桑德拉•胡森特鲁特•格雷(Cassandra Huysentruyt Grey)说：“自己得多花点时间打造赏心悦目形象。突然身处红地毯时，你会顿感压力山大；自己感觉不爽，肢体语言与脸上表情就会显露无遗。”

There’s something inordinately stressful about preparing for formal occasions, even if it’s just the annual office shindig. So imagine the extra pressure stars face at the Golden Globes, next week’s Baftas, and the Oscars, \colorbox{green}{when} the imaginative detail that looked so good \colorbox{green}{when}$^{\ref{sen:1}}$ rehearsed with the hairdresser has the potential to morph into a “red carpet \colorbox{yellow}{fail}$^{\ref{voc:2}}$”?

即便只是一场办公室寻常年度盛会，为正式场合打理形象也是压力巨大。所以明星大腕参加金球奖(Golden Globes)、英国电影和电视艺术学院奖(Baftas)以及奥斯卡(Oscars)等重量级颁奖典礼时遭受的压力有多大也就不难理解了：当初与专用发型师对每个富含想象力的细节排练得无可挑剔，很可能最后演变成“红地毯上的大出丑”。


“Beauty on the red carpet is unique,” adds Grey, who has an insight into its challenges. Married to Paramount Pictures chairman and chief executive, Brad Grey, she has \colorbox{yellow}{sat through countless speeches and walked} \colorbox{yellow}{innumerable red carpets}$^{\ref{voc:3}}$. “The lighting is pretty bad,” she says, “and even the most confident woman suddenly finds herself in the uncomfortable position of being in what is \colorbox{yellow}{essentially}$^{\ref{voc:4}}$ a petting zoo. Beauty — whether it’s lips or hair — can be an aide to get in character.”

“为走红毯美容化妆是很独特的。”格雷补充道，她对参加各种典礼面临的挑战有着深刻理解。作为派拉蒙影业公司(Paramount Pictures)董事长兼CEO布莱德•格雷(Brad Grey)的妻子，她聆听过无数的演讲、走过数不清的红毯。“舞台灯光特别强烈刺目。”她说，“置身在宠物动物园似的环境中，即便平时最为自信的女人也会突然之间变得不知所措。美容化妆（不管是嘴唇还是头发）可以为适应角色助上一臂之力。”

Luckily, there are plenty of aides — \colorbox{green}{from} the eyebrow specialist, \colorbox{green}{to} the body-polish expert \colorbox{green}{to} the eyelash person \colorbox{green}{to}$^{\ref{sen:2}}$ the plastic surgeon. \colorbox{green}{It does, as the saying goes, take a village}$^{\ref{sen:3}}$. Naturopath and facialist Dr Nigma Talib, who looks after Sienna Miller and Penélope Cruz and who has clinics in London and at the Four Seasons Doheny in Los Angeles, starts getting calls from the agents several weeks before. If the “Talent” is still eating sugar (imagine!), Talib gets them off it, and cuts out gluten, dairy and alcohol to reduce any signs of facial “bloating”. “You don’t have time to get blood tests back,” she explains, “but everything starts in the gut, so I prescribe good probiotics and sleep support.” (Usually a herbal supplement called Ashwagandha, \colorbox{green}{which Talib says is great for fatigue and} \colorbox{green}{lack of concentration}$^{\ref{sen:4}}$ — maybe it helps you to sit through all the speeches). On the \colorbox{yellow}{actual}$^{\ref{voc:5}}$ day she’ll give her clients a facial that includes a chemical peel, LED light therapy, and applications of hyaluronic acid and jellyfish collagen. (Not one of her vegan clients has complained about the jellyfish, but then this is Hollywood).

幸运的是，增色添彩的帮手比比皆是——从美眉与身体磨砂专家、睫毛师再到整容医师，应有尽有。俗话说得好：众心成城。专为大明星西耶娜•米勒(Sienna Miller)以及佩内洛普•克鲁兹(Penélope Cruz)服务的理疗师及面部美容师塔利布医生(Dr Nigma Talib)在伦敦及洛杉矶多希尼四季酒店(Four Seasons Doheny in Los Angeles)都开有美容诊所，一般都是好几周前就接到客户的预约电话。如果该明星客户仍在吃糖（假想而已！），塔利布就不让他们再吃它，而是让他们停吃麸质与奶制品以及戒酒以便使脸部“消肿”。“诸位不可能在短时间内把血液等各项指数降至正常。”她解释道，“但所有毛病都始于内脏，所以我给对方开了益生素以及让其保持充足睡眠。”（她通常给客户开印度人参，这种草药补剂对缓解疲劳与治愈注意力不集中疗效显著——可让对方精神抖擞听完整个演讲）。客户来就诊时，她会给对方做包括医学换肤、LED光疗以及施用玻尿酸(Hyaluronic Acid)与水母胶原蛋白(jellyfish collagen)在内的脸部美容。（对于使用水母胶原蛋白，她的素食客户中没有人抱怨，但这是在巨星云集的好莱坞）。

Yes, yes, yes, but what about the \colorbox{yellow}{hard stuff}$^{\ref{voc:6}}$? I hear you ask. Where do they all go for their Botox and facelifts? In LA, ever since the Kardashians made him famous, \colorbox{green}{Dr Simon Ourian is the go-to in Beverly Hills}$^{\ref{sen:5}}$ for that model-perfect look, and has 1.4m Instagram followers to show for it. Santa Monica’s Dr Karyn Grossman is a little more discreet and popular with middle-aged male \colorbox{yellow}{celebrities}$^{\ref{voc:7}}$. In London, the name that all the top facialists refer their clients to for injectables is Dr Tapan Patel.

对！这些难伺候的巨星大腕怎么办？你们会这么提问。他们去哪儿注射肉毒杆菌与做面部拉皮术呢？在洛杉矶，卡戴珊姐姐(the Kardashians)让西蒙•奥里安医生(Dr Simon Ourian)声名远扬后，其美容诊所就成了比弗利山庄(Beverly Hills)那些意欲打造完美模特形象的好莱坞明星的“圣地”，奥里安医生拥有的Instagram粉丝高达140万人。洛杉矶圣莫尼卡(Santa Monica)的卡里恩•格罗斯曼(Dr Karyn Grossman)医生则行事低调，在中年男星中有超高人气。伦敦的明星若是注射美容的话，面部顶级美容师无一例外都会向其推荐塔潘•帕特尔医生(Dr Tapan Patel)。

Perhaps surprisingly, according to Huysentruyt Grey, it’s the younger women who are tweaking and fixing. “They’re altering their looks seemingly because it makes them feel more comfortable in their skin, but it also makes them more bankable.”

胡森特鲁特•格雷说，年轻女性青睐整形美容(tweaking and fixing)，这一点有些出乎意料。“她们整容的原因似乎是增添自信心，而且还让自己更具吸金力。”

\colorbox{green}{When it comes to make-up}$^{\ref{sen:6}}$, however, there has been a movement towards stealthy understatement: as anyone who’s ever had to attend a black-tie event understands, one spritz of hairspray too many, one overdone smoky eye, and you’ve instantly added 10 years to your natural age.

但说起施用粉黛，如今的发展趋势则是悄无声息地化淡妆：任何着正式晚礼服参加社交活动的人都清楚，喷过多发胶或是熏眼过度，立马会显得比实际年龄老上十岁。

Of course, natural doesn’t really mean barefaced. Huysentruyt Grey. \colorbox{green}{cites “the quintessential natural style of European women who}$^{\ref{sen:7}}$ seem to have made that confident, effortless polish their signature,” as an example. Isabelle Huppert at the Golden Globes \colorbox{yellow}{exemplified}$^{\ref{voc:8}}$ the look — a flawless complexion, dark red lip, and classic side-parted natural hair. Michelle Williams (pictured below), Julianne Moore, Cate Blanchett \colorbox{yellow}{equally}$^{\ref{voc:9}}$, never seem to make a bad move.

当然，天然模样并不真正意味着素颜。胡森特鲁特•格雷列举了“典型天然风格的欧洲女性（她们似乎崇尚那种增添自信心、不费力妆扮）”的例子。参加金球奖颁奖典礼的伊萨贝尔•于佩尔(Isabelle Huppert)就是展现上述形象的活生生例子——完美的肤色、殷红色的嘴唇以及传统的自然偏分发型。米歇尔•威廉姆斯、朱丽安•摩尔以及凯特•布兰切特似乎也从不越雷池半步。

“There’s a \colorbox{yellow}{temptation}$^{\ref{voc:10}}$ to try and match the gravitas of the event with hair and make-up,” says Alex Babsky, Lancôme’s UK make-up ambassador (Lancôme has been the beauty partner of Bafta for 17 years, which easily end up looking overly regal).”

“我们参加庄重活动时，似乎总想收拾发型与浓妆重彩。”兰蔻(Lancôme)英国彩妆大使阿列克斯•巴布斯基(Alex Babsky)说（兰蔻已连续17年担任英国电影与电视艺术学院奖颁奖典礼官方化妆品合作伙伴，所以最终的颁奖典礼很容易尽显奢侈豪华）。

Babsky has made up everyone from Sarah Jessica Parker to Lupita Nyong’o and Thandie Newton and prefers a matt finish foundation generally (he loves Lancôme’s Teint Idole Ultra, £30). “When you can’t be sure of the lighting it’s always a \colorbox{yellow}{safer bet}$^{\ref{voc:11}}$: an all over glowy finish can look sweaty in the wrong conditions.”

巴布斯基为从莎拉•杰西卡•帕克(Sarah Jessica Parker)到露皮塔•尼永奥(Lupita Nyong'o)及桑迪•牛顿 (Thandie Newton)在内的众多明星美妆，他通常爱用亚光粉底（matt finish foundation，他酷爱售价30英镑的兰蔻超轻透持久粉底液 (Teint Idole Ultra)）。“当你不清楚舞台灯光实际效果时，这样做始终较为保险：美妆得太过红光满面在糟糕的典礼场合会给人大汗淋漓的感觉。”

Equally, hair needs to be kept simple. “If the dresses are couture and very formal, it’s less ageing to play down the hair,” says Nicola Clarke, who has looked after Kate Winslet, Cate Blanchett and Daisy Ridley for Bafta, and \colorbox{green}{is rarely seen without a can of}$^{\ref{sen:8}}$ R+Co Vicious Strong Hold Flexible Hairspray (\$29) and Color Wow’s Root Cover Up (£28.50) for \colorbox{yellow}{stray greys}$^{\ref{voc:12}}$.

发型同样得尽可能简约。“穿高档正装的话，简单发型就显得比实际年龄年轻。”尼古拉•克拉克(Nicola Clarke)说，他负责为参加英国电影与电视艺术学院奖颁奖典礼的凯特•温丝莱特(Kate Winslet)、凯特•布兰切特以及黛茜•雷德利(Daisy Ridley)美妆，对于间或稀疏灰白头发的明星，他总是使用R+Co Vicious Strong Hold Flexible Hairspray强力柔性发胶与Color Wow可掩盖发根再生的Root Cover Up。

But is it \colorbox{yellow}{worth the effort}$^{\ref{voc:13}}$? “Recently there’s been a subtle shift in LA with a lot of women feeling they’re somehow \colorbox{yellow}{diminishing their position}$^{\ref{voc:14}}$ as a feminist by \colorbox{yellow}{putting effort into their look}$^{\ref{voc:15}}$,” says Grey. “I guess their point is, is it politically correct to wear millions of dollars of jewellery or to be spending so much time choosing a dress? But it’s a very serious part of the industry — you’re representing a multibillion-dollar movie franchise, or a designer brand, and the images that result will affect your career. Plus, it’s Hollywood, and you’re in the entertainment business! Let’s bring some joy and fun.”

但是，如此大动干戈是否值得？“最近，洛杉矶时尚界悄然发生了变化：很多女性觉得对自我形象如此兴师动众，从某种程度上会降低自己女权主义者的地位。”格雷说，“我觉得实质问题是：佩戴价值几百万美元的首饰或是在穿着上大把烧钱是否在政治立场上正确？而这又是时尚界的重头戏——这些女明星是票房几十亿美元电影产业与知名品牌的形象代言人，其市场效应反过来也会影响自己的职业生涯。除此之外，这儿是巨星云集的好莱坞，这些女明星身处娱乐业中心！还是让我们给世界带些开心快乐吧。”

\section{笔记}
\subsection{句子}
\begin{enumerate}
\item So imagine the extra pressure stars face at the Golden Globes, next week’s Baftas, and the Oscars, when the imaginative detail that looked so good when rehearsed with the hairdresser has the potential to morph into a “red carpet fail”?\label{sen:1}

这句话里面有两个when，可以分解为So imagine \dots the Oscars, \colorbox{green}{when} the imaginative detail \colorbox{green}{\{\dots\}} has the potential to morph into a “red carpet fail” 和 \colorbox{green}{\{\dots\}}中的 the imaginative detail that looked so good \colorbox{green}{when} rehearsed with the hairdresser


\item Luckily, there are plenty of aides — \colorbox{green}{from} the eyebrow specialist, \colorbox{green}{to} the body-polish expert \colorbox{green}{to} the eyelash person \colorbox{green}{to} the plastic surgeon.\label{sen:2}

从什么到什么，要列举某几件事物的时候，用多个to，from \{\dots\},to \{\dots\},to \{\dots\}

\item It does, as the saying goes, take a village.\label{sen:3}

这种俗语我们自己写作的时候应该用不上，但是能长见识

\item which Talib says is great for fatigue and lack of concentration\label{sen:4}

这里体现了中英文的差距，这里不能翻译为“药方有益于疲劳和注意力不集中”，而应该翻译为“这种草药补剂对缓解疲劳与治愈注意力不集中疗效显著”；同理中文翻译成英文请不要添加冗余的单词

\item In LA, ever since the Kardashians made him famous, Dr Simon Ourian is the go-to in Beverly Hills for that model-perfect look, and has 1.4m Instagram followers to show for it.\label{sen:5}

这个句子长，但是找到主干就容易理解了，In \{\dots\} famous, Dr Simon Ourian is \{\dots\}, and has \{\dots\}

\item When it comes to make-up, however, there has been a movement towards stealthy understatement\label{sen:6}

When it comes to sth.的意思是“说起”、“when the specified matter is under consideration”；可以用原句的顺序，When it comes to make-up, there \dots；也可以放在后面，it pays to be proactive \colorbox{green}{when it comes to} your health

\item Huysentruyt Grey. cites “the quintessential natural style of European women who seem to have made that confident, effortless polish their signature,” as an example.\label{sen:7}

找到主干，Huysentruyt Grey. cites “\colorbox{green}{\{\dots\}}” as an example；然后\colorbox{green}{\{\dots\}}里面有一个从句，European women who seem to have made that confident, effortless polish their signature

\item “If the dresses are couture and very formal, it’s less ageing to play down the hair,” says Nicola Clarke, who has looked after Kate Winslet, Cate Blanchett and Daisy Ridley for Bafta, and is rarely seen without a can of R+Co Vicious Strong Hold Flexible Hairspray (\$29) and Color Wow’s Root Cover Up (£28.50) for stray greys.\label{sen:8}

这个句子长，分成三个部分，第一部分是Nicola Clarke说了一句话；第二部分是，Nicola Clarke, who has looked after Kate Winslet, Cate Blanchett and Daisy Ridley for Bafta；第三部分是Nicola Clarke, who is rarely seen without \{\dots\} for stray greys

\end{enumerate}

\subsection{词汇与词组}
\begin{enumerate}
\item \textbf{thrown into}\label{voc:1}

文中，You’re thrown into this high-pressure environment，用了被动，表达出一种强迫的，被动的情景；throw作为动词，有两个常用的意思

\begin{itemize}
\item 动作上的把某物扔出去
\item 使某事突然进入某种状态；例句：he threw all her emotions into turmoil;the bond market was thrown into confusion.

\end{itemize}



\item \textbf{fail}\label{voc:2}

fail可以是名词也可以是动词，fail作为动词时
\begin{itemize}
\item 未成功达到目标例句：he failed in his attempt to secure election | [不定式] : they failed to be ranked in the top ten
\item 疏于做某事；例句：the firm failed to give adequate risk warnings.
\item 坏了，不正常工作了；例句：a lorry whose brakes had failed.

\end{itemize}

\item \textbf{sat through countless speeches} and \textbf{walked innumerable red carpets}\label{voc:3}

\item \textbf{essentially}\label{voc:4}
used to emphasize the basic, fundamental, or intrinsic nature of a person or thing；也就是
\begin{itemize}
\item 本质上
\item 非常
\item 大体上
\end{itemize}


\item \textbf{actual}\label{voc:5}

两个含义，有差别
\begin{itemize}
\item existing in fact; real；事实上
\item existing now; current；目前的
\end{itemize}

\item \textbf{hard stuff}\label{voc:6}

难伺候的巨星大腕，hard的常见意思有
\begin{itemize}
\item solid, firm, and rigid; not easily broken, bent, or pierced；坚硬的；例句：the slate broke on the hard floor
\item done with a great deal of force or strength；通过大力气完成的；例句：a hard whack
\item requiring a great deal of endurance or effort；需要很大忍耐和努力的；例句：she found it hard to believe that he could be involved
\end{itemize}

\item \textbf{celebrities}\label{voc:7}

娱乐方面和运动方面的明星

\item \textbf{exemplified}\label{voc:8}

\begin{itemize}
\item be a typical example of；是某种事物的例子；例句：the best dry sherry is exemplified by the fino of Jerez
\item illustrate or clarify by giving an example；通过举例说明某些事情；例句：he exemplified his point with an anecdotedone with a great deal of force or strength
\end{itemize}

\item \textbf{equally}\label{voc:9}

\begin{itemize}
\item 平均地；例句：distribute sth. equally to sb.
\item 同样地；例句：to be equally right
\item 此外；例句：equally, he could have a point
\end{itemize}

\item \textbf{temptation}\label{voc:10}

the desire to do something, especially something wrong or unwise；偏向贬义

\item \textbf{safer bet}\label{voc:11}

bet本来意思是
\begin{itemize}
\item 动词，语言上的打赌；例句：I bet this place is really spooky late at night
\item 动词，用钱的打赌；例句：he bet on baseball games
\item 名词，赌博；例句：she had a bet on the Derby
\end{itemize}
但是这里翻译为“这样做始终较为保险”，是因为bet的意思被safer改变了

\item \textbf{stray greys}\label{voc:12}

grey本来意思是
\begin{itemize}
\item 颜色灰色；例句：his hair was grey and wispy
\item 无趣的，没有什么特别的；例句：the grey daily routine
\item not accounted for in official statistics；例句：the grey economy
\end{itemize}
在这里用了复数，变成指代灰色头发的人；另一种形容词变指代，是加the，如poor是形容词，the poor是贫穷的人

\item \textbf{worth the effort}\label{voc:13}

worth既可以是形容词也可以是名词，形容词的时候
\begin{itemize}
\item equivalent in value to the sum or item specified；例句：jewellery worth £450 was taken
\item sufficiently good, important, or interesting to be treated or regarded in the way specified；例句：the museums in the district are well worth a visit
\end{itemize}
名词的时候
\begin{itemize}
\item the level at which someone or something deserves to be valued or rated；例句：they had to listen to every piece of gossip and judge its worth
\item the amount that could be achieved or produced in a specified time；例句：the companies have debts greater than two years' worth of their sales
\end{itemize}


\item \textbf{diminishing their position}\label{voc:14}

diminish的意思是某物变少，例句：[with object] : the new law is expected to diminish the government's chances | [no object] : the pain will gradually diminish；但是这里延伸为cause to seem less impressive or valuable

\item \textbf{putting effort into their look}\label{voc:15}

effort的意思是坚定的，有力的尝试；有几个常用的词汇
\begin{itemize}
\item make an effort；例句：make an effort to do some kind of abdominal exercise
\item make every (or spare no) effort，意思是尝试所有可能达成某事；例句：the doctor spared no effort in helping my father
\end{itemize}


\end{enumerate}

\end{document}