%!TEX program = xelatex
\documentclass[UTF8]{ctexart}
\pagestyle{plain}
\begin{document}
\tableofcontents

\section{new}
\begin{itemize}
\item Courtesy demands reciprocity, as the Chinese saying goes

\item Revelations on that subject in US congressional hearings this week should give pause to anyone who cares about democracy 最近美国国会听证会上曝光的情况，应该让关心民主体制的所有人深思

\item A traditional Chinese gong clangs. Adoring sighs break out as a red curtain is pulled aside. Behind it are China's newest ambassadors to the west - a pair of chubby black-and-white bears sitting on their haunches munching bamboo stalks

\item Most important of all, the EU’s underlying cohesion \underline{has turned out} to be greater than \underline{anticipated}. Against a backdrop of squabbles over migration quotas or financial risk-sharing in the euro zone, politicians on both sides of the Channel \underline{underestimated} the strength of the consensus on the EU’s basic business model.
\end{itemize}

\section{FT.com - Nov 14 - Donald Trump’s dangerous delusions on trade}
The White House is the adult who prioritises keeping trade flowing and Congress is the fractious adolescent who keeps demanding confrontation with trading partners and refuses to sign new deals.

白宫是优先保持贸易流动的成年人，国会是不断要求与贸易伙伴对抗并拒绝签署新协议的叛逆青少年。

\section{FT.com - Nov 16 - Face up to responsibility, Facebook and friends}
\underline{In the 12 years since Mark Zuckerberg launched Facebook}, the global media landscape has changed beyond recognition.

在马克扎克伯格(Mark Zuckerberg)推出Facebook以来的12年里，全球媒体版图发生了天翻地覆的变化

\section{FT.com - Nov 9 - Donald Trump's victory challenges the western democratic model}
\underline{Barring a protean change of personality}, Mr Trump’s victory appears to represent a challenge to the western democratic model.

除非特朗普的个性发生突变，否则他的胜选看起来对西方民主模式代表着一个挑战。

\section{FT.com - Oct 17 - What China can learn from its Venezuela blow}
One way forward would be for Chinese and western-backed development institutions to work together. Their qualities — the singularity of purpose and speed of execution of China and the due diligence of the World Bank, Asian Development Bank and others — could \underline{combine for optimum results}. But this can only be a partial solution because ...

未来的一条出路是中西方的发展机构携手合作。双方的特点——中国的目的性和执行速度与世行、亚洲开发银行(Asian Development Bank)等机构的尽职调查——结合起来可能实现最优结果。但这只是一部分解决方案，解决不了全部问题，因为...

\section{FT.com - July 27 - A dangerous new phase in cyber aggression}
As for diplomacy, the US has had some success — it struck a deal with China to refrain from cyber espionage that has at least helped. However, this was possible because Beijing was unwilling to be shown up and anxious to preserve its commercial interests. The US has no such leverage over Vladimir Putin. Sanctions against Russia are already in place. \underline{As for} deterrence, \underline{there is only so far} rhetoric \underline{can go}.

至于外交方面，美国取得了一些成功——与中国达成的不进行网络间谍活动的协议至少有所帮助。然而，中美之所以能达成协议，是因为北京方面不愿意被揭穿，而且急于要保护自己的商业利益。但美国对弗拉基米尔•普京(Vladimir Putin)没有这样的筹码。对俄罗斯的制裁早已就位。至于威慑，打打嘴仗的效果始终有限

\section{FT.com - Aug 24 - Eurozone looks beyond the Brexit vote}
The latest data suggesting the eurozone had shrugged off the Brexit vote came yesterday. Purchasing managers’ indices for the single currency area, a reasonably reliable indicator of future growth, showed a composite measure of confidence holding up well in August, \underline{consistent with} the economy turning in another solid performance in the third quarter with growth around 0.3 or 0.4 per cent.

显示欧元区已摆脱英国退欧公投阴影的最新数据昨日出炉。欧元区采购经理人指数(PMI)显示，8月综合信心指数强劲，符合欧元区经济第三季度的稳健表现——增速约为0.3\%或0.4\%。PMI是评估未来增长的一个相当可靠的指标。

The reading for France, whose economy stalled in the second quarter, \underline{was particularly encouraging, suggesting it will} bounce back in the third.

法国的数据尤其令人鼓舞，表明第二季度陷入停滞的法国经济将在第三季度实现反弹。

Mr Hollande and Mr Renzi are right to argue for more fiscal stimulus. The eurozone’s fiscal pact is already \underline{on the way to} being \underline{as much of} a laughing stock \underline{as} its predecessors, \underline{as evidenced by} the European Commission’s decision not to levy fines from Spain and Portugal for missing their deficit targets by handsome margins.

奥朗德与伦齐主张进行更多财政刺激是正确的。欧元区财政协定正在像之前的协定一样沦为笑柄——欧盟委员会(European Commission)决定不就西班牙和葡萄牙财政赤字大幅超标对这两国处以罚款就是例证。

Yet to raise their sights from avoiding disaster to celebrating a marked improvement, keeping things as they are will \underline{not be sufficient}.

然而要让他们的目光从避免灾难转向庆祝显著的改进，维持现状是不够的。


\section{The Economist - July 2nd - July 8th/Charlemagne}
\begin{itemize}
\item But draw the camera back and a different picture emerges
\end{itemize}

\section{The Economist - July 9nd - July 15th/225m reasons for China's leaders to worry}
\begin{itemize}
\item Before the late 1990s China barely had a middle class. In 2000, 5m households made between \$11,500 and \$43,000 a year in current dollars; today 225m do. By 2020 the ranks of the Chinese middle class may well outnumber Europeans.
This stunning development has boosted growth around the world and transformed China. \underline{Paddyfields have given way to skyscrapers, bicycles to traffic jams}. An inward-looking nation has grown more cosmopolitan: last year Chinese people took 120m trips abroad, a fourfold rise in a decade. \underline{A vast} Chinese chattering class has \underline{sprung up on social media}.

\item Many pundits believe that China is \underline{an exception to} this pattern
\end{itemize}

\section{The Economist - July 9nd - July 15th/225m reasons for China's leaders to worry}
Mr Kagame himself has admitted that leapfrogging has limits. Drones can transport blood, but they can’t transport doctors, who need roads. Solar panels will help people light their homes without burning kerosene, but they will not replace the functioning grid that manufacturers need. Nor will clever technology firms do away with the need for well-drafted regulation and the ruleoflaw.

\section{FT.com - Aug 12th - Learn from experience for the best industrial plan}
An industrial strategy is a good idea, \underline{provided that} it is built around sectors where the UK has a comparative advantage and where the government is an important player, either as a provider of development finance or as a customer.

产业战略是个好想法——前提是它围绕着英国具备比较优势、且政府是重要参与者（要么作为开发融资的提供者，要么作为客户）的行业

Capitalism \underline{thrives on} animal spirits \underline{but occasionally} creates monsters. \underline{The challenge for} policymakers is to encourage the one while nailing the other.

资本主义的繁荣依赖于动物精神，但有时也会造出怪物。政策制定者面临的挑战在于鼓励动物精神同时抓住怪物。

\section{Report of Fu}
Overnight social media star/overnight sensation：大火的明星；go viral 火了（动词）

The enthusiasm of one Chinese swimmer after winning a bronze has made her an overnight social media star. 一个中国游泳运动员赢得铜牌后的热烈表现让她成为中国社交媒体红人。- BBC

Online meme 表情包；fete 追捧；spoof 搞笑模仿（动词）

Fans feted her as “Primordial Girl” in online memes and viral videos spoofing her exuberant expressions. 粉丝追捧她为“洪荒女孩”，模仿她热烈的表情做了一系列表情包和红遍网络的视频。- WSJ

Flooded with：被刷屏

Weibo was flooded with emoticons made of Fu. 微博被傅园慧的表情刷屏。- SCMP

Heartfelt 真诚的（同 authentic，candid）；also-ran 落败的（例句中引申改为 also-swam）

Two heartfelt interviews was all it took to transform 20-year-old Chinese swimmer Fu Yuanhui from also-swam to social media star. 两个真诚的采访让 20 岁的中国游泳运动员傅园慧从落败者一下变成了社交媒体红人。- Variety

Expressive：表情丰富的；barometer for：...的体现

Her expressive face is the perfect barometer for how we feel watching the Olympic Games. 她丰富的的表情完美体现了我们观看奥运会感受。- NYMag

Endear 吸引（粉丝）；make animated faces 做表情；exuberance 充满能量、激情（名词）；

It is her exuberance out of the water that has endeared her to fans. Rather than mere happiness at her performances, Ms. Fu, 20, exhibits something closer to pure joy, bouncing around and making animated faces. 她出水后的热情吸引了众多粉丝。20 岁的傅园慧展现的不仅是她对自己发挥的满意，还有一种接近纯粹快乐的东西。她跳来跳去，做各种表情。- NYT

Gasp：倒吸一口气

Fu, who had thought that she had failed to win a medal, gasped joyfully when told by a television reporter that she had actually won bronze. 以为自己没得奖牌的傅园慧在听记者说自己其实得了铜牌后，开心得倒吸了一口气。- Reuters

Deadpan：假装严肃地说笑话；Ready：诙谐的

She deadpanned that her “arms are too short” after learning that she had finished just one-hundredth of a second off the silver-medal winning time. 在听说自己以 0.01 秒的劣势输给了银牌得主时，傅园慧严肃地说，我的手臂太短了。- NYT

Fu had a ready explanation about why she couldn’t top third place on Tuesday. Her arms, she said, were “too short.” 对于自己周二的比赛为什么没能比第三名更进一步，傅园慧有个诙谐的解释。我的手臂太短了，她说。- The Guardian

Return to the spotlight 重新回到人们关注中心；bop 激动地跳来跳去

如果你只能记住一个词，请一定要学会 authentic，表示“真性情”，true to one's own personality, spirit, or character

\section{The Economist USA - August 13/Schumpeter}
\underline{Gone are the days when} geeks wore shapeless T-shirts to prove that they didn’t care about physical appearances.

\section{FT.com - Sep 23 - Facebook philanthropy hubris offers hope}
Just as important is the Zuckerbergs’ use of a limited liability partnership rather than a more rigid tax exempt foundation as the entity through which to give. This provides greater flexibility in deciding whether they provide grants or invest for profit in medical programmes.

同样重要的是，扎克伯格利用有限责任公司作为捐赠的实体，而非更严格的可以减免税收的慈善基金会。这让他们可以更加灵活地决定是提供补助，还是对医学项目进行营利性投资。

\section{FT.com - Sep 29 - America's dystopian presidential debate}
\underline{In the absence of} a dramatic turnround in skills training, that number is set to rise further. \underline{So too, will} the politics of irate venting that has fuelled Mr Trump’s candidacy.

在技能培训没有显著改善的情况下，这一比例势必进一步上升。发泄愤怒的政治策略——特朗普凭借这种策略获得候选人资格——也将更有用武之地。

What can be done? The responsibility of a leader is to be straight with the people. \underline{Neither trade, nor technology, should be blamed for} Washington’s failure to equip its workforce for the 21st century.

怎么做呢？领导人有责任向民众说清实情。政府未能帮助其劳动人口掌握应对21世纪所需的知识技能，这不应该怪贸易，也不应该怪技术。

\section{FT.com - Sep 13 - Investment threats in a changing climate}
Climate change is now an unavoidable business issue. In an excellent paper last week, BlackRock, the world’s largest fund manager, set out some of the ways that investors can reduce their exposure to the risks and benefit from the opportunities that it creates. The paper is a landmark in the rising awareness of the issue among mainstream investors. \underline{It is one thing} when a philanthropic fund with assets of a few hundred million takes a stand on climate issues, \underline{quite another} when the warnings come from a company with about \$4.9tn under management.

气候变化现在是一个躲不开的商业问题。在上周的一篇精彩报告中，全球最大的基金管理公司贝莱德(BlackRock)阐述了投资者减少气候变化问题给他们带来的风险及利用相关机遇的几种途径。这篇报告具有十分重大的意义，说明主流投资者不断增强对气候变化问题的意识。一家资产只有几亿美元的慈善基金在气候问题上表达立场是一回事，而一家管理着4.9万亿美元资产的公司发出警告则是另一回事。

\section{FT.com - Oct 10 - Ivory trade drives elephants to the brink of extinction}
There are two strategies to arrest the catastrophe. \underline{Unfortunately}, they pull in opposite directions.

有两种策略可以阻止大象灭绝。遗憾的是，这两种策略可以说是背向而驰。


\section{FT.com - Oct 8 - Artificial intelligence is too important to leave unmanaged}
\underline{Scarcely a day passes without some startling news emerging about} the latest advances in smart machines, whether it is digital assistants, robot surgeons, or self-driving cars. Venture capital money is seemingly pouring into any start-up that can sprinkle the magic acronym AI over its pitch deck.

如今，几乎每天都会有一些关于智能机器最新进展的惊人消息，不管是数字助理、机器人外科医生还是自动驾驶汽车。风投资金似乎正大量涌入所有那些在融资宣讲书(pitch deck)上带有AI这个具有魔力的字眼的初创企业。

“\underline{We are at a big data tipping point more than an AI tipping point},” he says. “The challenge is to apply these techniques in a space that is commercially interesting and where there is access to big data sets.”

“与其说我们处于一个人工智能的转折点，不如说我们处于一个大数据的转折点，”他表示，“我们面临的挑战在于把这些技术应用于一个在商业上有趣而且能够获取大数据的空间。”

\section{FT.com - Oct 11 - Harness the disruptive effects of artificial intelligence}
\underline{One does not have to be} a believer in some dystopian future \underline{to} recognise the benefits of such research. The landscape is dotted with signs of what happens when clever algorithms are left to their own devices, from the self-driving Tesla car that crashed to Microsoft’s out-of-control chatbot on Twitter.

就算你不是反乌托邦主义者也会认识到此类研究的好处。我们已经多次看到当人们让聪明的算法自己操控设备时会发生什么——从特斯拉(Tesla)自动驾驶汽车撞毁，到微软聊天机器人在Twitter上失控。

\section{FT.com - Oct 13 - UK faces €20bn Brexit divorce bill in Brussels budget wrangle}
The sheer size of the upper estimate, which some EU officials reckon is too low, \underline{threatens to} poison the break-up and derail a Brexit transition and trade deal, according to several senior European figures involved in the process.

据参与相关过程的多名欧洲资深人士介绍，上述估计上限（一些欧盟官员还认为太低）的惊人数额，有可能对退欧过程造成负面影响，使英国退欧过渡和贸易协议难产。


\section{She Follows The Money}
我们将结束克林顿式的腐败，重塑政府的尊严与诚信。
We are going to end the Clinton Corruption and restore dignity and honesty to government service.

去年，整个美国，所有城市，无论大小，整体凶杀率上涨了10\%。
Across the entire nation, for cities of all sizes, small and large, the homicide rates rose by more than 10\% last year.

美利坚合众国已经到了最危险的时候。
This is a national crisis.

然后，在我们本周的辩论中，她指责了整个国家，她还说我们的执法部门都是有偏见的。这意味着她认为我们的警察和人民都是有偏见的种族歧视者。
Then, in our debate this week, she accusses the entire country, including all of law enforcement, of “implicit bias,” – essentially suggesting that everyone, including our police, are basically racist and prejudiced.

我们只想要安全平和的生活，她却敌视所有勤劳的美国人民。
She has nothing but hostility in her heart for hardworking Americans, of all backgrounds, who just want to live in safety, security and peace.

我们将废除国家核心课程标准，我们还将彻底解决上学难的问题，不会让任何一个穷苦的拉丁裔和非裔小孩失去受教育的机会。我们会让每个小孩都有机会实现自己的美国梦：享受良好的教育以及找到合适的工作岗位。
We are also going to end common core and offer school choice to every disadvantaged child – including every poor Hispanic and African-American child in America. We will put every American kid on the ladder of American success: a great education, and a great job.

众志成城，我们可以实现所有梦想。
Together, we can accomplish anything we want.

那么，在11月8日，你必须投出你关键的一票。早一点投票吧，因为提前投票已经开始了。
But that means you need to show up and vote on November 8th - and it means you need to start voting early. Early voting is already underway.

你可以出门拜访、也可以打电话、还可以在街上为我们拉票。把我们的爱分享给所有美国人民。想打败这个腐朽的政治系统，你必须让大家听到你的心声，走出家门，投出你宝贵的一票。你还可以登录我们的竞选网站，查询如何给我们提供帮助。
You have to knock on doors. You have to pick up that phone. You have to campaign on the streets. Spread the love that we have in this room to the people of our country. To beat the system, you have to lift your voice, pound the pavement, and get out the vote. Visit our website to find out how you can help.

为了每一个被遗忘的男人、女人以及小孩，为了实现正义，这是一次伟大的机会，也是最后一次。
You have one last magnificent chance to deliver justice for every forgotten man, woman and child in this nation.

别让它溜走，别让这个机会从你手中溜走。为了你的家庭，为了你的家乡，为了你的国家，起来，每个人被迫发出最后的吼声。
Don’t let it slip away. Don’t let this chance go. Stand up and be heard – for your family, for your city, for your country.

11月8日，我们会让世界看到美国重获新生，美国将会变得比任何时候都要辉煌、壮大。
This November 8th, we are going to show the whole world that America is Back – Bigger and Better and Stronger than Ever Before.

如果所有人都能一起团结合作，默契如一人，信仰同一个上帝，同时向着一面国旗敬礼，这样我们就能实现任何梦想。
Imagine what our country could accomplish if we started working together as One People, under One God, saluting One American Flag.

是时候和苦涩的过去说再见了。现在我们，美国人民，要迎接一个崭新的、不分你我的、辉煌的未来。
It is time to break with the bitter failures of the past, and to embrace a new, inclusive and prosperous American future.

\section{nov28p11}
This year will all but certainly be the hottest since 1880, when NASA’s records begin. If so, 2015 will break a record that was set only in 2014. Every single year so far this decade has been hotter than every single year before 1998. In short: thinking caps should replace hair shirts, and pragmatism should replace green theology

\section{nov21p76}
“Low Life” (1991) painted a vivid portrait of life in New York’s Lower East Side in the 19th and early 20th centuries. But New York is a city that wears its transformations on its sleeve. Paris does not, although it has been altered again and again by the twin forces of revolution and civic planning, as Mr Sante ably shows

\section{nov28p66}
For years outsiders have seen Belgium as a microcosm of Europe: first, in its expression of the dream that domestic differences can be dissolved in a federalist soup; subsequently as an example of north-south mistrust. Recent events provide a third prism

\section{dec5p95}
nowhere near
Yet the bitter truth is that the world is nowhere near the sort of carbon-pricing regime that would keep greenhouse gases at tolerable levels. Politics is the biggest obstacle. There are nonetheless some ways to make carbon prices more politically palatable. First,
Second, Finally. As solutions go, these three can be criticised for lacking elegance and simplicity. it would give individual exporters to carbon-pricing countries an incentive to become greener, irrespective of whether their own government had adopted a carbon price

\section{dec5p88}
To avoid this fate, and increase the chances of producing a strong successor, business families need to grasp two things. The first is that, The second thing that business founders must grasp is that, broaden their experience, boost their self-confidence

vice versa/embrace the hardship/grumble/last but not least/so forth/sniggering/bragged to sb./munch/to take a selfie with sb.

That the rich are getting richer, and the richest are getting richer fastest, is beyond doubt 

\section{“Spain’s democracy is about to turn 40. How well has it worn?”}
“MANY OF THE photos seem older than they are. In black and white, they show Spaniards wrapped in overcoats, the men with sideburns, the women with perms, voting in a referendum on a new constitution on December 6th 1978. Some 67 \% of the electorate turned out, of whom 87 \% voted yes, setting the seal on their country’s swift move to democracy after the death of Francisco Franco, its long-standing military dictator.”
\end{document}